Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 intro.tex
some updates

Distributed systems are notoriously hard to test. This is due to many well-known sources of \emph{nondeterminism}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and message losses, and interaction with clients and external services.
%
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute. A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases.

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, stress testing, fault injection, and chaos testing) are unable to capture and control all the aforementioned sources of nondeterminism, which causes the most tricky backs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money and many dissatisfied customers.

>>>>

Distributed systems are notoriously hard to test. This is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with clients and external services.
%
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute. A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases.

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money and many dissatisfied customers.
